### 2010-12-22 doc/manuals/user_interface/ui-job.tex
Adding short description of GRID_GLOBAL_JOBID to UI manual. Fixing dependencies in Makefile.

\begin{framed}
%% This depends on the middleware flavour. Some flavours do not accept listing
%% the job session directory (CREAM).
   Every job ID is a valid URL for the job session directory. You can
   always use it to access the files related to the job, by using data
   management tools (see Chapter~\ref{sec:dm}).
\end{framed}

>>>>

\begin{framed}
   Usually job ID is a valid URL for the job session directory. You can
   always use it to access the files related to the job, by using data
   management tools (see Chapter~\ref{sec:dm}).

   There may be exception for some computational services like CREAM 
   which do not support listing job session directory.
\end{framed}

\begin{framed}
   For advanced computational jobs which may need to communicate their 
   presence to some service outside there may be need for knowing own
   job ID. For jobs accepted by ARC computationsl services this information
   may be found in local (for job executable) environment variable 
   GRID\_GLOBAL\_JOBID. One need to take into account that this ID may be 
   different from one provided by arcsub. Example is ID provided by
   A-REX computational service. That service provides OGSA BES 
   compatible interface for job management and ID contains XML document
   according to OGSA BES specifications.
\end{framed}
